Viscous Transport in Eroding Porous Media

### 2019-10-07 docs/transport/erosion_transport.tex
working through edits

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo[inline]{Bryan is here}
In line with our previous work~\cite{qua-moo2018}, we use two meshes to
simulate erosion. The integral equation is solved by discretizing the
boundary of the geometry at a set of collocation points distributed
equally in arclength (Section~\ref{sec:spatialDiscretization}).
Depending on the proximity of the target point to the source points, the
quadrature rule is either the trapezoid rule or the Barycentric
quadrature rule (Section~\ref{sec:bary}).  The selection algorithm that
determines which quadrature method is applied is described in
Section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
are eroded a single time step by using a {\thL}
discretization~\cite{hou-low-she1994, moore2013self}.  The time stepping methods for
erosion and passive particles are described in Section~\ref{sec:time}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\label{sec:spatialDiscretization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Since we use a BIE formulation, we only have to discretize the
one-dimensional boundary of the domain.  Therefore, we easily resolve
complex geometries, and differentiation is performed with spectral
accuracy in Fourier space.  We discretize each eroding body $\gamma_k$
with $N_\iin$ points and discretize the outer wall $\Gamma$ with
$N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ and
$\gamma_k$ are denoted by $\yy_j^0$ and $\yy^k_j$, respectively.  The
discretization points are initially distributed evenly in arclength, and
this equispacing is maintained for the entire simulation by using the
{\thL} formulation.  In addition, we apply
regularization~\cite{qua-moo2018} to slightly smooth the corners that
inevitably develop during erosion.

Given the discretization points of $\bd\Omega$, applying the trapezoid
rule results in the collocation method for~\eqref{eqn:BIE} 
\begin{subequations}
\label{eqn:trapLinearSystem}
  \begin{alignat}{3}
  \UU_\ell &= \sum_{j=1}^{N_\out} 
    w^0_j D(\yy^0_\ell,\yy^0_j) \eeta_j^0 +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j +
  \sum_{j=1}^{N_\out} w^0_j N_0(\yy^0_\ell,\yy^0_j)\eeta_j^0 
    \nonumber \\
  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^0_\ell) + 
  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^0_\ell),
    &&\hspace{-60pt} \ell = 1,\ldots,N_\out, \\
%
  \mathbf{0} &= \sum_{j=1}^{N_\out} 
    w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j^0 +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j \nonumber \\
  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^m_\ell) + 
  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^m_\ell),
    &&\hspace{-60pt}\ell = 1,\ldots,N_\iin, \: m=1,\ldots,M, \\
%
  \llambda_m &= \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m \eeta^m_j,
  \quad \xi_m = \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m
    (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
    &&\hspace{-60pt} m=1,\ldots,M,
\end{alignat}
\end{subequations}
where $w^k_j$ are quadrature weights that depend on $N_\iin$, $N_\out$,
and the lengths of $\gamma^k$ and $\Gamma$, and $D$ is the kernel of the
Stokes double-layer potential defined in
equation~\eqref{eqn:velocityDLP}.  The linear
system~\eqref{eqn:trapLinearSystem} is a well-conditioned second-kind
integral equation that is solved iteratively with GMRES.  If the number
of discretization points is sufficiently large, then the solution
of~\eqref{eqn:trapLinearSystem} is an accurate approximation of the
density function, Stokeslets, and rotlets.   Then, if $\xx \in \Omega$
is sufficiently far from $\bd\Omega$, an approximation of the velocity,
deformation tensor, and vorticity due to the double-layer potential is
found by applying the trapezoid rule to \eqref{eqn:velocityDLP},
\eqref{eqn:deformationDLP}, and~\eqref{eqn:vorticityDLP}, respectively.
In particular,
\begin{align}
  \label{eqn:trap}
  \uu(\xx) &= \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j, \\
%
  \ssigma(\xx) &= \sum_{j=1}^{N_\out} w^0_j \mathbf{D}_\ssigma(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j \mathbf{D}_\ssigma(\xx,\yy^k_j)
  \eeta^k_j, \\
%
  w(\xx) &= \sum_{j=1}^{N_\out} w^0_j D_\omega(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D_\omega(\xx,\yy^k_j)
  \eeta^k_j.
\end{align}
The contributions due to the Stokeslets and rotlets require no
quadrature and are easily included in the velocity, deformation tensor,
and vorticity.  Finally, to compute the shear stress, we apply the
trapezoid rule with Fourier differentiation to approximate the jump
term~\eqref{eqn:deformationJump} of the deformation tensor, and then the
tensor is applied to the normal and tangent vectors as defined in
equation~\eqref{eqn:shearStress}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature Formulas}
\label{sec:bary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While the trapezoid rule is spectrally accurate for smooth, periodic
functions~\cite{tre-wei2014}, the derivative of the integrands grows as
the target point $\xx$ approaches $\bd\Omega$ and so the error bound
depends on the location of the target point. Therefore, if the trapezoid
rule is applied when bodies are in near-contact, or when a layer
potential is evaluated at a point close to $\bd\Omega$, then the results
become unreliable and the simulation ultimately becomes unstable.  We
thus desire a quadrature method whose error bound does not depend on the
target location.

We showed in Sections~\ref{sec:DLPcomplex} and~\ref{sec:gradDLPcomplex}
that the velocity, shear stress, and vorticity of the double-layer
representation can all be written as the sum of Cauchy integrals and its
first two derivatives.  Therefore, we can accurately compute the
velocity, shear stress, and vorticity at any target location if we
develop a quadrature rules with a uniform error bounded for Cauchy
integrals and its derivatives~\eqref{eqn:cauchy}.  Ioakimidis et
al.~\cite{ioa-pap-per1991} developed quadrature rules, that we call {\em
Barycentric quadrature rules}, to compute Cauchy integrals and their
derivatives with an error bound that is independent of $x \in \CC$.
Then, Barnett et al.~\cite{bar-wu-vee2015} used these quadrature rules
to compute the Stokes double-layer potential representation of the
velocity~\eqref{eqn:velocityDLP}, and we briefly summarize their method.
Then, we build on this work to accurately compute the gradient of the
Stokes double-layer potential so that we form the shear stress and
vorticity.

We present the quadrature rules for a simply-connected interior domain
$\Omega \subset \CC$, with any point $a \in \Omega$, and we consider the
target points $x \in \Omega$ and $x \in \Omega^c$. Then, these
quadrature rules can be applied to individual components of a
multiply-connected domain to compute layer potentials of a porous media.
The method starts with an underlying quadrature rule, and we use the
spectrally accurate trapezoid rule.  Since the quadrature points are
uniformly distributed, the quadrature weights are $w_j = L/N$,
$j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.

@@

To compute the shear stress and vorticity, we require a Barycentric
quadrature rule for $v''(x)$.  The derivation is largely based on the
work of Ioakimidis et al.~\cite{ioa-pap-per1991} (see equation (2.12)).
We start with the second derivative of the Cauchy integral theorem
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x).
\end{align}
For the interior case, $x \in \Omega$, we use the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n = 2,3,\ldots. \\
    \end{array}
  \right.
\end{align}
Combining this identity with the Cauchy integral representation of
$v''(x)$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
This integrand is constructed so that it is bounded for all $x \in
\Omega$, and applying the trapezoid rule, we have
\begin{align}
  0 \approx  \sum_{j=1}^{N} 
      \frac{2v^{-}(y_j) - v''(x)(y_j-x)^2 - 2v(x) - 2(y_j-x)v'(x)}
      {(y_j-x)^3} w_j,
\end{align}
where the accuracy is independent of $x$.  Solving for $v''(x)$, the
Barycentric quadrature rule for the interior second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, \quad x \in \Omega.
\end{align}
For the exterior case, $x \in \Omega^c$, we start with the identity
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x}\, dy. 
\end{align}
Combining this identity with the Cauchy integral representation of
$v''(x)$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
    \frac{2v^+(y) - 2v(x) - 2(y-x)v'(x) + (y-a)^{-1} (x-a) (y-x)^2 v''(x)}
    {(y-x)^3}.
\end{align}
As in the interior case, the integrand is chosen so that it is bounded
for all $x \in \Omega^c$.  Therefore, after applying the trapezoid rule
and solving for $v''(x)$, we have the Barycentric quadrature rule for
the exterior second derivative
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}, 
    \quad x \in \Omega^c.
\end{align}
The quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$,
and theses are computed using the quadrature rules in
equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
and~\eqref{eqn:BaryvprimeExterior}. In Section~\ref{sec:results}, these
quadrature rules are used to form stable eroding simulations of
nearly-touching grains, and to study dynamics of the flow in regions
arbitrarily close to eroding grains.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Efficiently Applying the Quadrature}
\label{sec:fmm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
By using the Barycentric quadrature rule, the velocity, shear stress,
and vorticity are computed with an error that is bounded independent of
the target location. However, applied directly, it requires
$\mathcal{O}(N^2)$ operations.  By using a fast summation method, such
as the fast multipole method (FMM)~\cite{gre-rok1987}, this cost can be
reduced to $\mathcal{O}(N)$ operations.  However, the Barycentric
quadrature rules require several $N$-body calculations, and they must be
done for each component of $\bd\Omega$ individually.  The resulting cost
would be prohibitive, so we introduce a hybrid method that combines the
Barycentric quadrature rule and the trapezoid rule.  Note that the
source points of the layer potential is always one of the eroding bodies
or the outer wall, but the target point can either be on another
component of $\bd\Omega$ or it can be in the fluid bulk $\Omega$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In line with our previous work~\cite{qua-moo2018}, we use two meshes to
simulate erosion. The integral equation is solved by discretizing the
boundary of the geometry at a set of collocation points distributed
equally in arclength (Section~\ref{sec:spatialDiscretization}).
Depending on the proximity of the target point to the source points, the
quadrature rule is either the trapezoid rule or the Barycentric
quadrature rule (Section~\ref{sec:bary}).  The criteria that determines
which quadrature method is applied is described in
Section~\ref{sec:fmm}.  Once the shear stress is computed, the bodies
are eroded a single time step by using a {\thL}
discretization~\cite{hou-low-she1994, moore2013self}.  The time stepping
methods for erosion and passive particles are described in
Section~\ref{sec:time}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\label{sec:spatialDiscretization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Since we use a BIE formulation, we only need to discretize the
one-dimensional boundary of the domain.  Therefore, we easily resolve
complex geometries, and differentiation is performed with spectral
accuracy in Fourier space.  We discretize each eroding grain $\gamma_k$
with $N_\iin$ points and discretize the outer wall $\Gamma$ with
$N_\out$ points.  The $j^{th}$ discretization point on $\Gamma$ and
$\gamma_k$ are denoted by $\yy_j^0$ and $\yy^k_j$, respectively.  The
discretization points are initially distributed evenly in arclength, and
this equispacing is maintained throughout the entire simulation by using
the {\thL} formulation.  In addition, we apply
regularization~\cite{qua-moo2018} to slightly smooth the corners that
inevitably develop during erosion.

Given the discretization points of $\bd\Omega$, the trapezoid rule
results in the collocation method for~\eqref{eqn:BIE}
\begin{subequations}
\label{eqn:trapLinearSystem}
  \begin{alignat}{3}
  \UU_\ell &= \sum_{j=1}^{N_\out} 
    w^0_j D(\yy^0_\ell,\yy^0_j) \eeta_j^0 +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
    w^k_j D(\yy^0_\ell,\yy^k_j) \eeta^k_j +
  \sum_{j=1}^{N_\out} w^0_j N_0(\yy^0_\ell,\yy^0_j)\eeta_j^0 
    \nonumber \\
  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^0_\ell) + 
  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^0_\ell),
    &&\hspace{-60pt} \ell = 1,\ldots,N_\out, \\
%
  \mathbf{0} &= \sum_{j=1}^{N_\out} 
    w^0_j D(\yy^m_\ell,\yy^0_j) \eeta_j^0 +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
    w^k_j D(\yy^m_\ell,\yy^k_j) \eeta^k_j \nonumber \\
  &\quad+\sum_{k=1}^M S[\llambda_k,\cc_k](\yy^m_\ell) + 
  \sum_{k=1}^M R[\xi_k,\cc_k](\yy^m_\ell),
    &&\hspace{-60pt}\ell = 1,\ldots,N_\iin, \: m=1,\ldots,M, \\
%
  \llambda_m &= \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m \eeta^m_j,
  \quad \xi_m = \frac{1}{2\pi} \sum_{j=1}^{N_\iin} w_j^m
    (\yy^m_j - \cc_m)^\perp \cdot \eeta^m_j,
    &&\hspace{-60pt} m=1,\ldots,M,
\end{alignat}
\end{subequations}
where $w^k_j$ are quadrature weights that depend on $N_\iin$, $N_\out$,
and the lengths of $\gamma^k$ and $\Gamma$, and $D$ is the kernel of the
Stokes double-layer potential defined in
equation~\eqref{eqn:velocityDLP}.  Since the kernel is smooth, the
diagonal terms $D(\yy_j^m,\yy_j^m)$ are replaced with the appropriate
curvature-dependent limiting term.  The linear
system~\eqref{eqn:trapLinearSystem} is a well-conditioned second-kind
integral equation that is solved iteratively with GMRES.  If the number
of discretization points is sufficiently large, then the solution
of~\eqref{eqn:trapLinearSystem} is an accurate approximation of the
density function, Stokeslets, and rotlets.   Then, if $\xx \in \Omega$
is sufficiently far from $\bd\Omega$, an approximation of the velocity,
deformation tensor, and vorticity due to the double-layer potential is
found by applying the trapezoid rule to \eqref{eqn:velocityDLP},
\eqref{eqn:deformationDLP}, and~\eqref{eqn:vorticityDLP}, respectively.
In particular,
\begin{align}
  \label{eqn:trap}
  \uu(\xx) &= \sum_{j=1}^{N_\out} w^0_j D(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D(\xx,\yy^k_j) \eeta^k_j, \\
%
  \ssigma(\xx) &= \sum_{j=1}^{N_\out} w^0_j \mathbf{D}_\ssigma(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j \mathbf{D}_\ssigma(\xx,\yy^k_j)
  \eeta^k_j, \\
%
  w(\xx) &= \sum_{j=1}^{N_\out} w^0_j D_\omega(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin} w^k_j D_\omega(\xx,\yy^k_j)
  \eeta^k_j.
\end{align}
The contributions due to the Stokeslets and rotlets require no
quadrature and are easily included in the velocity, deformation tensor,
and vorticity.  Finally, to compute the shear stress, we apply the
trapezoid rule with Fourier differentiation to approximate the jump
term~\eqref{eqn:deformationJump} of the deformation tensor, and then the
tensor is applied to the normal and tangent vectors as defined in
equation~\eqref{eqn:shearStress}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature Formulas}
\label{sec:bary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While the trapezoid rule is spectrally accurate for smooth, periodic
functions~\cite{tre-wei2014}, the derivative of the integrand grows as
the target point $\xx$ approaches $\bd\Omega$. The result is an error
bound depends on the location of the target point. Therefore, if the
trapezoid rule is applied when bodies are in near-contact, or if a layer
potential is evaluated at a point close to $\bd\Omega$, then the result
become unreliable and the simulation ultimately becomes unstable.  We
thus desire a quadrature method whose error bound does not depend on the
target location.

We showed in Sections~\ref{sec:DLPcomplex} and~\ref{sec:gradDLPcomplex}
that the velocity, shear stress, and vorticity of the double-layer
representation can all be written as the sum of Cauchy integrals and its
first two derivatives.  Therefore, we can accurately compute the
velocity, shear stress, and vorticity at any target location by using a
quadrature rule with a uniform error bound for Cauchy integrals and its
derivatives~\eqref{eqn:cauchy}. Ioakimidis et al.~\cite{ioa-pap-per1991}
developed quadrature rules, that we call {\em Barycentric quadrature
rules}, to compute Cauchy integrals and their derivatives with an error
bound that is independent of $x \in \CC$.  Then, Barnett et
al.~\cite{bar-wu-vee2015} used these quadrature rules to compute the
Stokes double-layer potential representation of the
velocity~\eqref{eqn:velocityDLP}, and we briefly summarize their method.
Then, we extend their work to compute the second derivative so that the
shear stress and vorticity can be computed with a uniform error bound.

We present the quadrature rules for a simply-connected interior domain
$\Omega \subset \CC$, with any point $a \in \Omega$, and we consider the
target points $x \in \Omega$ and $x \in \Omega^c$. Then, these
quadrature rules can be applied to individual components of a
multiply-connected domain to compute layer potentials of a porous media.
The method starts with an underlying quadrature rule, and we use the
spectrally accurate trapezoid rule with $N$ points.  Since the
quadrature points are uniformly distributed, the quadrature weights are
$w_j = L/N$, $j=1,\ldots,N$, where $L$ is the length of $\bd\Omega$.

@@

To compute the shear stress and vorticity, we require a Barycentric
quadrature rule for $v''(x)$.  The derivation is largely based on the
work of Ioakimidis et al.~\cite{ioa-pap-per1991} (see equation (2.12)).
We start with the second derivative of the Cauchy integral theorem
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x).
\end{align}
For the interior case, $x \in \Omega$, we use the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n = 2,3,\ldots. \\
    \end{array}
  \right.
\end{align}
Combining this identity with the Cauchy integral representation of
$v''(x)$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
This integrand is constructed so that it is bounded for all $x \in
\Omega$, and applying the trapezoid rule, we have
\begin{align}
  0 \approx  \sum_{j=1}^{N} 
      \frac{2v^{-}(y_j) - v''(x)(y_j-x)^2 - 2v(x) - 2(y_j-x)v'(x)}
      {(y_j-x)^3} w_j,
\end{align}
where the accuracy is independent of $x$.  Solving for $v''(x)$, the
Barycentric quadrature rule for the interior second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, \quad x \in \Omega.
\end{align}
For the exterior case, $x \in \Omega^c$, we start with the identity
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x}\, dy. 
\end{align}
Combining this identity with the Cauchy integral representation of
$v''(x)$, we have
\begin{align}
  0 = \frac{1}{2\pi i} \int_{\bd\Omega} 
    \frac{2v^+(y) - 2v(x) - 2(y-x)v'(x) + (y-a)^{-1} (x-a) (y-x)^2 v''(x)}
    {(y-x)^3}.
\end{align}
As in the interior case, the integrand is chosen so that it is bounded
for all $x \in \Omega^c$.  Therefore, after applying the trapezoid rule
and solving for $v''(x)$, we have the Barycentric quadrature rule for
the exterior second derivative
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}, 
    \quad x \in \Omega^c.
\end{align}
The quadrature rule for $v''(x)$ requires the values $v(x)$ and $v'(x)$,
and theses are computed using the quadrature rules in
equations~\eqref{eqn:BaryvInterior},~\eqref{eqn:BaryvExterior},~\eqref{eqn:BaryvprimeInterior},
and~\eqref{eqn:BaryvprimeExterior}. In Section~\ref{sec:results}, these
quadrature rules are used to form simulations of nearly-touching eroding
grains, and to study dynamics of the flow in regions arbitrarily close
to eroding grains.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Efficiently Applying the Quadrature}
\label{sec:fmm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo[inline]{Bryan is here}
By using the Barycentric quadrature rule, the velocity, shear stress,
and vorticity are computed with an error that is bounded independent of
the target location. However, applied directly, it requires
$\mathcal{O}(N^2)$ operations.  By using a fast summation method, such
as the fast multipole method (FMM)~\cite{gre-rok1987}, this cost can be
reduced to $\mathcal{O}(N)$ operations.  However, the Barycentric
quadrature rules require several $N$-body calculations, and they must be
done for each component of $\bd\Omega$ individually.  The resulting cost
would be prohibitive, so we introduce a hybrid method that combines the
Barycentric quadrature rule and the trapezoid rule.  Note that the
source points of the layer potential is always one of the eroding bodies
or the outer wall, but the target point can either be on another
component of $\bd\Omega$ or it can be in the fluid bulk $\Omega$.
